---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TravelBehaviorQinghaiData

<!-- badges: start -->
<!-- badges: end -->

The `TravelBehaviorQinghaiData` is an r package created by first-year PhD student [Haoran Xu](https://github.com/Horan517) for the final course project ["TBQT"](https://github.com/Horan517/TBQTSEM) of ["GEOG712 - Reproducible Research Workflow"](https://github.com/paezha/Reproducible-Research-Workflow/tree/master), taught by Dr. Antonio Paez at McMaster University, Canada.

The package contains the data for the paper title "Assessing the influence of tourists’ perceived travel environment and their travel behavior on travel satisfaction using structural equation models (SEM): a case of Qinghai-Tibet Plateau". The data was collected between July 21 and August 4 in 2022 through distributing online and on-site questionnaires by the research group of [Dr. Huaxiong Jiang](https://www.researchgate.net/scientific-contributions/Huaxiong-Jiang-2157090528). It was designed to collect local and non-local tourists' travel behavior and their perceptions of travel environment on Qinghai-Tibet Plateau. The complete questionnaire, originally in Chinese and translated in English, is stored in `data-raw` folder as a bilingual version.

## Installation

You can install the development version of `TravelBehaviorQinghaiData` from [GitHub](https://github.com) with:

```{r}
if(!require(remotes)){
    install.packages("remotes")
    library(remotes)
}
remotes::install_github("Horan517/TravelBehaviorQinghaiData")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(TravelBehaviorQinghaiData)

data(TBQT)

head(TBQT)
summary(TBQT)

```

# How to cite

Xu, H. (2024). TravelBehaviorQinghaiData: Data for the paper "Assessing the influence of tourists’ perceived travel environment and their travel behavior on travel satisfaction using structural equation models (SEM): a case of Qinghai-Tibet Plateau". https://github.com/Horan517/TravelBehaviorQinghaiData

``` latex
@Manual{TravelBehaviorQinghaiData,
  title = {Data for the paper "Assessing the influence of tourists’ perceived travel environment and their travel behavior on travel satisfaction using structural equation models (SEM): a case of Qinghai-Tibet Plateau"},
  author = {Haoran Xu},
  year = {2024},
  note = {R package version 1.1},
  url = {https://github.com/Horan517/TravelBehaviorQinghaiData}
}
```
