---
title: "data_prep"
author: "Haoran Xu"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The file of `TBQT_raw.xlsx` is the Excel file that contained all of the questionnaire results collected for the paper. It contains one sheet, as follows:

- Original Q Results (n = 814): the raw data

This markdown file is created to clean the data and convert it into `.RData` file to be used in modelling and subsequent analysis. 

Load the packages needed to preprocess the data:
```{r}
library(tidyverse)
library(readxl)
library(here)
library(lavaan)
```

```{r}
# Define the file paths using here()
input_path <- paste0(here(), "/data-raw/TBQT_raw.xlsx")
output_path <- paste0(here(), "/data-raw/TBQT_raw.csv")

# Converting .xlsx file into .csv file while deleting its first row of question descriptions
TBQT <- readxl::read_excel(input_path)

# Define the variable names
colnames(TBQT) <- c(
  "numbering", "type", "gender", "age", "residence", "income", "edu_lvl", 
  "profession", "household_size", "dri_lic", "num_cars", 
  "purpose1", "purpose2", "purpose3", "purpose4", "purpose5", 
  "self_drive", "other_drive", "pub_trans", "bicycle", "walking", 
  "frequency_travel", "planned_travel_time", 
  "attraction_type1", "attraction_type2", "attraction_type3", 
  "daily_t", "daily_d", "exp_lvl", "num_phones", 
  "if_connected_network", "stability_network", 
  "daily_phone_use_t", "frequency_phone_use", "daily_devices_use_t", 
  "device_proficiency", 
  "value_e_devices1", "value_e_devices2", "value_e_devices3", 
  "value_e_devices4", "value_e_devices5", "value_e_devices6", 
  "value_e_devices7", "value_e_devices8", "value_e_devices9", 
  "value_e_devices10", "travel_safety1", "travel_safety2", 
  "travel_safety3", "travel_safety4", "travel_safety5", 
  "travel_safety6", "travel_safety7", "sati_lvl", 
  "prss_allevi", "hlt_impro", "ta_envi1", "ta_envi2", 
  "ta_envi3", "ta_envi4", "ta_envi5", "ta_envi6", 
  "r_envi1", "r_envi2", "r_envi3", "r_envi4", "r_envi5"
)
```

Convert all the cells of missing data (value == -2) into NA:
```{r}
TBQT <- TBQT %>%
  mutate(across(everything(), ~ ifelse(. == -2, NA, .)))
```

Adjust the values for some dummy variables and some variables that used 5-point Likert scales:
```{r}
# convert some binary variables that originally used {1, 2} into {0, 1}
TBQT <- TBQT %>%
  mutate(
    gender = ifelse(gender == 1, 0, 1),
    dri_lic = ifelse(dri_lic == 2, 0, 1),
    if_connected_network = ifelse(if_connected_network == 2, 0, 1)
  )

# the options of ordinal variable `num_cars` in the questionnaire are set wrong and here needs to re-assign its values
TBQT <- TBQT %>%
  mutate(
    num_cars = case_when(
      num_cars == 4 ~ 0,
      num_cars == 5 ~ 4,
      TRUE ~ num_cars
    )
  )

# reverse the order of more ordinal variables that used 3-point or 5-point Likert scale
TBQT <- TBQT %>%
  mutate(
    stability_network = 4 - stability_network,
    frequency_phone_use = 4 - frequency_phone_use,
    device_proficiency = 5 - device_proficiency
  )

columns_to_reverse <- c(
  "exp_lvl", "value_e_devices1", "value_e_devices2", "value_e_devices3", 
  "value_e_devices4", "value_e_devices5", "value_e_devices6", 
  "value_e_devices7", "value_e_devices8", "value_e_devices9", 
  "value_e_devices10", "travel_safety1", "travel_safety2", 
  "travel_safety3", "travel_safety4", "travel_safety5", 
  "travel_safety6", "travel_safety7", "sati_lvl", 
  "prss_allevi", "hlt_impro", "ta_envi1", "ta_envi2", 
  "ta_envi3", "ta_envi4", "ta_envi5", "ta_envi6", 
  "r_envi1", "r_envi2", "r_envi3", "r_envi4", "r_envi5"
)

TBQT <- TBQT %>%
  mutate(across(all_of(columns_to_reverse), ~ 6 - .))
```

Next, two variables are re-categorized. 

One is `residence` variable, which will be re-categorized into "local = 1 or non-local = 0" based on people's answers that captured where they came from on a certain Chinese administrative district level (provinces/autonomous regions/municipalities). Those administrative districts on the Qinghai-Tibet Plateau (mainly from Qinghai Province, Xizang Autonomous Region, and part of Sichuan Province and Gansu Province) will be categorized as "local", while other places will be "non-local".

The other variable is `profession`, which will be re-categorized into "flexible = 1 or inflexible = 0" based on their different profession characteristics. Professions as "Farmers (Herdsmen); Self-Employed; Freelancer; Student; Other" will be regarded as "flexible", while other types (Civil Servant; Engineering Specialist; Teacher; Full-time Driver; Researcher; Company Employee) will be counted as "inflexible".

```{r}
# recategorizing `residence` variable
TBQT <- TBQT %>%
  mutate(
    # replacing all the "(空)" with NA
    residence = ifelse(residence == "(空)", NA, residence),
    
    # replacing those texts containing "Qinghai"/"Xizang""Sichuan - Ganzi" with 1, while others with 0
    residence = ifelse(
      str_detect(residence, "青海|西藏|四川-甘孜"), 1, 0
    )
  )

# recategoizing `profession` variable
TBQT <- TBQT %>%
  mutate(profession = case_when(
    profession %in% c(2, 4, 8, 9, 11) ~ 1,
    TRUE ~ 0
  ))
```

New summary of the dataframe:
```{r}
summary(TBQT)
```

Save to data folder:
```{r}
# Save the cleaned data as a CSV file
write_csv(TBQT, output_path)

# save to `data` folder 
usethis::use_data(TBQT
                  , overwrite = TRUE)
```
